\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-05-18 manuscript/main.tex
modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	deleted:    working-version-March-27-2024.pdf

@@

@@

We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed. Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market. We can denote the number of two types of brokerages by $\mathcal{B}_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{\mathcal{B}_{i, i}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}$. We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$.

@@

We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}. Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and let $L^B$ denote the set of broad searchers, defined as those individuals who consider a $\beta$ proportion of all available houses within their expansive search criteria. When $\beta = 1$ it means that they are searching for all the available houses in the whole city and $\beta < 1$ indicates a limited scope, possibly due to preferences or capacity constraints. Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$, and the expected number is given by $L^B_i = L^B \times \beta$.

@@

% here is my question using rigorous mathematical model and mathematical framework to:

% now formulate the assumption that other store's brokerage are homogenous and the brokerage $1$'s network effect is greater than other bokerage.

% now give me the first proposition that in equilibrium, the number of brokerage $1$'s share in the market is greater than the number of brokerage $1$'s proportion of number of stores. Besides, the brokerage $1$'s optimal choice of broekrage charge is greater than other brokerage

@@

Now we derive the cosumer surplus, which is:

>>>>

\textbf{Finish Theoretical Model by May 20th, Finish the Online Appendix, Empirical Finding by May 25th, and Finish the Discussion and Conclusion by May 30th.}

@@

 % I think this model does not evaculate the meaningful information from the paper, and the paper does not have anything interesting to say in this model.

@@

We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed. Assume that the sellers are indifferent among the brokerages and therefore, their chossing is only dependent on the proportion of stores in the market. We can denote the number of two types of brokerages by $\mathcal{B}_{1, i}$ and $B_{2, i}$, respectively and therefore, the number of houses listed in the brokerage $j$ is $\kappa_{i} \times \frac{\mathcal{B}_{i, i}}{\mathcal{B}_{i, 1} + \mathcal{B}_{i, 2}}$. We can assume that the price of the house is determined by the hedonic pricing model from various confounding factors that are determined by the community and unique characteristics of the housing, and we can denote it as $P_i$ that can be ranked and distributed over the range $[\underline{P}_i, \overline{P}_i]$. Sellers have a reservation price $\tilde{P}_i$ over the house they sell.

@@

We can inherent from the previous literature that there are broad searchers and narrow searchers in the market, \citep{10.1257/aer.20141772}. Specifically, we can assume that there are $L^N_i$ narrow searches that are only searching for the community $i$ and let $L^B$ denote the set of broad searchers, defined as those individuals who consider a $\beta$ proportion of all available houses within their expansive search criteria. When $\beta = 1$ it means that they are searching for all the available houses in the whole city and $\beta < 1$ indicates a limited scope, possibly due to preferences or capacity constraints. Correspondingly, $L^B_i$ represents the subset of broad searchers within community $i$, and the expected number is given by $L^B_i = L^B \times \beta$. We can denote the buyers' utility of owning the house by $U_{i, j}$

@@

The consumer surplus is then: $CS = \sum_{i=1}^M \sum_{j=1}^{\mathcal{N}} \int_0^{L_{i, j}} (U_{i, j} - P_i) dx$.

@@

This model is not good right now because there is no better way to conduct welfare analysis.
